---
title: "PROJECT_NAME Project Report"
author: "UM Bioinformatics Core"
date: "`r Sys.Date()`"
output:
        html_document:
            theme: readable
            toc: true
            toc_depth: 4
            toc_float: true
            number_sections: true
            fig_caption: true
            keep_md: true
bibliography: references_WAT.bib
csl: bioinformatics.csl
---

<!---
Can change this either in the .md or .Rmd document...

For docx output to get edits, change output field above to:
        word_document:
            toc: true
            toc_depth: 3
            fig_caption: true
            keep_md: true

Default HTML output:

        html_document:
            toc: true
            toc_depth: 3
            toc_float: true
            keep_md: true
--->

<!--- Allow the page to be wider --->
<style>
    body .main-container {
        max-width: 1200px;
    }
</style>

```{r echo = FALSE}
################################################################################
# Load Libraries
library(yaml)

# packages = data.frame(installed.packages())

# Read the config file
config = snakemake@config

# Set working directory to project dir
setwd(project_dir)

# Read the software environment version yaml
versions = yaml.load_file(snakemake@input[['versions']])


################################################################################
# Set things up you'll need downstream

diffex_info = snakemake@params[['diffex_model_info']]

contrasts = snakemake@params[['contrasts']]

exclude_diffex = typeof(contrasts) == 'character' && contrasts == ''

add_custom = snakemake@params[['add_custom']]

# factor_covs = config$covariates$factor

################################################################################
# Flags for showing particular sections

show_background_biology = TRUE
show_methods_wetlab = TRUE

show_background_samples = TRUE
show_methods_qc_sequencing = TRUE
show_results_qc = TRUE

show_appendix_qc = TRUE

if(exclude_diffex) {
    show_background_diffex = FALSE
    show_methods_diffex = FALSE
    show_results_diffex = FALSE
    show_appendix_diffex = FALSE
} else {
    show_background_diffex = TRUE
    show_methods_diffex = TRUE
    show_results_diffex = TRUE
    show_appendix_diffex = TRUE
}

if(add_custom){
    show_methods_custom = TRUE
    show_results_custom = TRUE
    show_appendix_custom = TRUE
} else {
    show_methods_custom = FALSE
    show_results_custom = FALSE
    show_appendix_custom = FALSE
}

```

*Contact:*

* Bioinformatics Core <bioinformatics@umich.edu>

<!---
Background
--->
```{r background_biology_section, child = 'child_background_biology.Rmd', eval = show_background_biology}
```

```{r background_samples_section, child = 'child_background_samples.Rmd', eval = show_background_samples}
```

```{r background_diffex_section, child = 'child_background_diffex.Rmd', eval = show_background_diffex}
```

<!---
Methods
--->
```{r methods_wetlab_section, child = 'child_methods_wetlab.Rmd', eval = show_methods_wetlab}
```

```{r methods_qc_sequencing_section, child = 'child_methods_qc_sequencing.Rmd', eval = show_methods_qc_sequencing}
```

```{r methods_diffex_section, child = 'child_methods_diffex.Rmd', eval = show_methods_diffex}
```

```{r methods_custom_section, child = 'child_methods_custom.Rmd', eval = show_methods_custom}
```

<!---
Results
--->

```{r results, child = 'child_results_qc.Rmd', eval = show_results_qc}
```

```{r results, child = 'child_results_diffex.Rmd', eval = show_results_diffex}
```

```{r results_custom_section, child = 'child_results_custom.Rmd', eval = show_results_custom}
```


# Follow-On

We are happy to answer any questions you may have and/or set-up a meeting to go over the results of your experiment.

In addition, if you would like more detailed output (e.g. FastQC and/or DESeq2 detailed output, etc.) please let us know. For information on the RNA-seq workflows and a comparison between available differential expression tools, please refer to [@Zhang2014].


# Citation

It is important to document use of each Biomedical Research Core Facility by investigators in publications. This facilitates efforts to obtain funding for our Cores and their continued functioning.

Please recognize the core’s contribution in the Acknowledgment section of your publications:

“We acknowledge support from the Bioinformatics Core of the University of Michigan Medical School’s Biomedical Research Core Facilities.”

If core staff have added scientific value to your project — made intellectual contributions in design, analysis and interpretation of data and/or manuscript writing, then please consider including them as co-authors in your publications.

<!---
Appendices
-->

<!-- # Appendices -->

<!-- ```{r appendix_qc_section, child = 'child_appendix_qc.Rmd', eval = show_appendix_qc} -->
<!-- ``` -->

<!-- ```{r appendix_diffex_section, child = 'child_appendix_diffex.Rmd', eval = show_appendix_diffex} -->
<!-- ``` -->

<!-- ```{r appendix_custom_section, child = 'child_appendix_custom.Rmd', eval = show_appendix_custom} -->
<!-- ``` -->

# References
