---
title: "`r project_name` Project Report"
author: "`r doc_author`"
date: "`r Sys.Date()`"
output:
        html_document:
            theme: readable
            toc: true
            toc_depth: 4
            toc_float: true
            number_sections: true
            fig_caption: true
            keep_md: true
bibliography: references_WAT.bib
csl: bioinformatics.csl
---

<!---
Can change this either in the .md or .Rmd document...

For docx output to get edits, change output field above to:
        word_document:
            toc: true
            toc_depth: 3
            fig_caption: true
            keep_md: true

Default HTML output:

        html_document:
            toc: true
            toc_depth: 3
            toc_float: true
            keep_md: true
--->

<!--- Allow the page to be wider --->
<style>
    body .main-container {
        max-width: 1200px;
    }
</style>

```{r include = FALSE}
################################################################################
# Load Libraries
library(yaml)


################################################################################
# Set things up you'll need downstream

config = snakemake@config
setwd(project_dir)

# Read the software environment version yaml
versions = yaml.load_file(snakemake@input[['versions']])


    show_methods_qc_sequencing = TRUE
    include_diffex = FALSE
    show_results_qc_align = TRUE
    show_results_qc_diffex = FALSE
    show_appendix_qc = TRUE

################################################################################
# Flags for showing additional optional sections

show_background_biology = snakemake@params[['add_background']]
show_background_samples = snakemake@params[['add_bg_samples']]
show_methods_prep = snakemake@params[['add_prep_description']]
show_follow_up = snakemake@config[['report_info']][['include_follow_up']] # note this is in config, others are params
custom_choices = unlist(strsplit(snakemake@params[['custom_sections']], ','))


if('methods' %in% custom_choices){
    show_methods_custom = TRUE
} else {
    show_methods_custom = FALSE
}
if('results' %in% custom_choices){
    show_results_custom = TRUE
} else {
    show_results_custom = FALSE
}
if('appendix' %in% custom_choices){
    show_appendix_custom = TRUE
} else {
    show_appendix_custom = FALSE
}


```

*Contact:*

* `r analyst_name` <`r analyst_email`>

<!---
Background
--->


# Background

```{r background_biology_section, child = 'child_background_biology.Rmd', eval = show_background_biology}
```

```{r background_samples_section, child = 'child_background_samples.Rmd', eval = show_background_samples}
```

<!---
Methods
--->


# Methods

```{r methods_prep_section, child = 'child_methods_prep.Rmd', eval = show_methods_prep}
```


## Pipeline

We use Snakemake [@Koster2012] to manage the bioinformatics workflow in a reproducible manner.

## QC and sequence alignment

The reads were trimmed using Cutadapt v`r versions[['cutadapt']][['cutadapt']]` [@Martin2011]. The reads were evaluated with FastQC [@Andrews2010] (v`r versions [['fastqc']][['fastqc']]`) to determine quality of the data. Reads were mapped to the reference genome `r config[['genome']]` (ENSEMBL), using STAR v`r versions[['rsem_star']][['star']]` [@Dobin2013] and assigned count estimates to genes with RSEM v`r versions[['rsem_star']][['rsem']]` [@Li2011]. Alignment options followed ENCODE standards for RNA-seq [@Dobin:STARmanual]. QC metrics from several different steps in the pipeline were aggregated by multiQC v`r versions[['multiqc']][['multiqc']]` [@Ewels2016]. 

```{r methods_custom_section, child = 'child_methods_custom.Rmd', eval = show_methods_custom}
```

<!---
Results
--->


# Results

<!---
Results QC + Alignment
--->

## QC

A detailed MultiQC report can be found at the following link:

```{r include = FALSE}
# Setup - copy multiqc html and link to it
cwd = sub("/ccmb/BioinfCore/ActiveProjects", "/nfs/med-bfx-activeprojects", getwd()) # TODO: when we remove /ccmb/ completely this will no longer be necessary, can just use getwd()
mqc_curr_path = file.path(project_dir, snakemake@input[['multiqc_html']])
mqc_copy_path = file.path(project_dir, report_dir, 'multiqc_linked_report.html')
copystatus = file.copy(mqc_curr_path, mqc_copy_path, overwrite = TRUE)

if(!copystatus){
  stop("Copying multiqc_linked_report.html to report dir failed.")
}

multiqc_link = './multiqc_linked_report.html'
```

### [Alignment Results - MultiQC report](`r multiqc_link`)

### Alignment Results - Summary Statistics

A summary of alignment statistics can be seen in the table below.


```{r include = FALSE}
####
# Set up summary table

# Determine whether or not to include % duplicates (can be problematic for AGC)
include_dups = snakemake@config[['report_info']][['include_pct_dups']]

# Read in multiqc tab-separated files
multiqc_gen_file = file.path(project_dir, snakemake@input[['multiqc_gen_stats']])
multiqc_star_file = file.path(project_dir, snakemake@input[['multiqc_star']])

multiqc_gen = read.table(multiqc_gen_file, header = TRUE, sep='\t', quote = "", stringsAsFactors = FALSE)
multiqc_star = read.table(multiqc_star_file, header = TRUE, sep='\t', quote = "", stringsAsFactors = FALSE)

# Subset STAR table to desired properties
star_keep_cols = c('Sample', 'total_reads', 'uniquely_mapped', 'uniquely_mapped_percent', 'avg_mapped_read_length', 'multimapped', 'multimapped_percent')
multiqc_star_subset = multiqc_star[,star_keep_cols]

# Subset general table to desired properties (just fastqc aligned percent-dup for now)
fastqc_aligned_pcdups = grep("^FastQC.*percent_duplicates$", colnames(multiqc_gen), value = TRUE)
multiqc_gen_subset = multiqc_gen[,c('Sample', fastqc_aligned_pcdups)] #Just grab Sample and aligned dup percentage from general stats

# Function to trim e.g. foo.bar.baz to baz (for simplifying column names)
trim_to_suffix = function(fullname) {return(sub(".*\\.", "", fullname))} # Trim to final suffix (all else captured by greedy . match)

# Clean column names
colnames(multiqc_gen_subset) = trim_to_suffix(colnames(multiqc_gen_subset))

# Remove rows with NA (in this case, everything except fastqc_aligned data rows)
multiqc_gen_subset = multiqc_gen_subset[complete.cases(multiqc_gen_subset),]

# Round the percent duplicate rates to nearest whole number
multiqc_gen_subset$percent_duplicates = round(multiqc_gen_subset$percent_duplicates, digits = 2)

# Percent duplicates are the only values derived from the general results table
# Merge the tables together only if dups included
if(include_dups){
  # Combine subset of STAR results table with subset of general results table
  multiqc_report_df = merge(multiqc_star_subset, multiqc_gen_subset, by = 'Sample', all = TRUE)
} else {
  multiqc_report_df = multiqc_star_subset
}


# Transform the column names
colnames(multiqc_report_df) = gsub("_", " ", colnames(multiqc_report_df))

# If more than 16 samples, scroll box needed.
# Scroll box is only created if height is defined
if(nrow(multiqc_report_df) > 16) {
  height.choice = '590px'
} else { height.choice = NULL }

multiqc_kable = kable(multiqc_report_df, row.names = FALSE, format.args = list(big.mark = ',', scientific = FALSE)) %>%
  kable_styling(bootstrap_options = c('striped', 'condensed')) %>%
  scroll_box(width = '100%', height = height.choice)

####
# Get subset of multiqc plots
mqc_plots_dir = file.path(project_dir, snakemake@params[['mqc_plots_dir']])
fig_regex_list = snakemake@config[['report_info']][['mqc_png_regex_list']]
select_mqc_plots = list()
for(re in fig_regex_list){
  this_selection = grep(re, list.files(mqc_plots_dir), value=TRUE, perl=TRUE)
  select_mqc_plots = c(select_mqc_plots, this_selection)
}
```

```{r echo = FALSE, results = 'asis', message = FALSE}
cat(multiqc_kable)

cat('&nbsp;')
cat('&nbsp;') #Some newlines to separate the table and figures
cat('&nbsp;')

for(fig in select_mqc_plots){
    fig_path = file.path(mqc_plots_dir, fig)
    cat(sprintf('![**Figure:** Selected MultiQC Figure](%s) \n\n', fig_path))
}
```

<!---
Results - Custom
-->
```{r results_custom_section, child = 'child_results_custom.Rmd', eval = show_results_custom}
```


```{r follow_up, child = 'child_follow_up.Rmd', eval = show_follow_up}
```


# Acknowledgement for Publication

`r acknowledgement_text`

<!---
Appendices
-->

<!-- # Appendices -->

<!-- ```{r appendix_qc_section, child = 'child_appendix_qc.Rmd', eval = show_appendix_qc} -->
<!-- ``` -->

<!-- ```{r appendix_custom_section, child = 'child_appendix_custom.Rmd', eval = show_appendix_custom} -->
<!-- ``` -->

# References
